Efficient ancestry and mutation simulation with msprime 1.0

### 2021-09-10 paper.tex
Comments from review

A important goal of the msprime development model is to maximise
accessibility for prospective users and contributors. However, it is important
to acknowledge that under-representation persists in population genetics,
especially in methodology and open-source software
development~\citep{trinkenreich2021women}. The authorship
of our paper reflects this with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive collaborative environment that helps to address these
inequalities in our field.

>>>>

An important goal of the msprime development model is to maximise
accessibility for prospective users and contributors. However, it is important
to acknowledge that under-representation persists in population genetics,
especially in methodology and open-source software
development~\citep{trinkenreich2021women}. The authorship
of our paper reflects this with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive and collaborative environment that helps to address these
inequalities in our field.
